NN_Accel_Heading

### 2024-03-14 Fish Data Analysis/NN_Accel_Heading.qmd
Playing around with using SD as limits

single_comp_data <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           # ### Used to remove every third point to reduce autocorrelation
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
                           group_by(Comp_ID) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup() %>% mutate(Type = "Single")

@@

min_dist <- 3
max_dist <- 100

@@

#Means graph
ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes( y = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA)) ), size = 1)+
  # geom_ribbon(aes(ymin = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) - se),
  #                 ymax = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) + se),
  #                 fill = interaction(Ablation, Darkness, sep =", ")),
  #             alpha = 0.25, colour = NA)+
  theme_classic() +
  ylim(-75,75) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle speed (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")+
  ggtitle(paste0("All Neighbors From ",min_dist," to ",max_dist))+ 
  guides(fill = FALSE)

>>>>

single_comp_data <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "S", "Single", "Jingle")) %>%
                           mutate(Darkness = ifelse(Darkness == "S", "Single", "Jingle")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("Single"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Single"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           # ### Used to remove every third point to reduce autocorrelation
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
                           group_by(Comp_ID) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup() %>% mutate(Type = "Single")

@@

sd <- 1.77

min_dist <- sd*0.5
max_dist <- sd*1.5

@@

#Means graph
ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes( y = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA)) ), size = 1)+
  # geom_ribbon(aes(ymin = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) - se),
  #                 ymax = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) + se),
  #                 fill = interaction(Ablation, Darkness, sep =", ")),
  #             alpha = 0.25, colour = NA)+
  theme_classic() +
  ylim(-100,100) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle speed (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")+
  ggtitle(paste0("All Neighbors From ",min_dist," to ",max_dist))+ 
  guides(fill = FALSE)
